Lattices of acyclic pipe dreams

### 2023-03-09 acyclicFacets/draft/latticePipeDreams.tex
improve Remark 5.11

\begin{remark}
\label{rem:linearExtensionsPartitionSubwordComplexA}
Before proving this theorem, we would like to make the following remarks about items~\eqref{item:convex} and~\eqref{item:cover}:
\begin{enumerate}
\setcounter{enumi}{0}
\item There are cases where $[e,\omega] \ne \linearExtensions(Q,\omega)$. Namely, some of the sets~$\linearExtensions(I)$ may not be included in~$[e,\omega]$, and may even not meet~$[e,\omega]$. See \cref{fig:counterExample1}.
%
%\begin{figure}[h]
%	\includegraphics[width=0.52\textwidth]{interval_not_contained1} \quad
%	\includegraphics[width=0.43\textwidth]{interval_not_contained2}
%	\caption{A facet of a subword complex~$\subwordComplex(Q, \omega)$ whose linear extensions all lie outside the interval~$[e, \omega]$.}
%	\label{fig:outOfInterval}
%\end{figure}
%
\begin{figure}[p]
	\centerline{\includegraphics[scale=.8]{counterExample1}}
	\caption{The sets~$\linearExtensions(I)$ (blue bubbles) are not always subsets of, and may even not meet~$[e,\omega]$ (green bubble).}
	\label{fig:counterExample1}
\end{figure}

\setcounter{enumi}{2}
\item Some of the sets~$\linearExtensions(I)$ may not be intervals. See \cref{fig:counterExample2}. Another example with~$\omega = \omega_\circ$ can be found in~\cite[Figure~9]{PilaudStump-brickPolytope}. 
%
\begin{figure}[p]
	\centerline{\includegraphics[scale=.8]{counterExample2}}
	\caption{The sets~$\linearExtensions(I)$ (blue bulles) are not always intervals.}
	\label{fig:counterExample2}
\end{figure}
\end{enumerate}
\cref{fig:counterExample1,fig:counterExample2} represent type~$A$ subword complexes.
As in~\cite{PilaudPocchiola, PilaudSantos-brickPolytope, PilaudStump-brickPolytope}, we thus use pseudoline arrangements on sorting networks to represent their facets (and we have represented their contact graphs together).
\end{remark}

>>>>

\begin{remark}
\label{rem:linearExtensionsPartitionSubwordComplexA}
Before proving it, we would like to make the following remarks about theorem.
\begin{enumerate}
\item While the sets~$\linearExtensions(I)$ are order convex, they may not be intervals. See \cref{fig:counterExample2}. Another example with~$\omega = \omega_\circ$ can be found in~\cite[Figure~9]{PilaudStump-brickPolytope}. 
%
\begin{figure}[p]
	\centerline{\includegraphics[scale=.8]{counterExample2}}
	\caption{The sets~$\linearExtensions(I)$ (blue bulles) are not always intervals.}
	\label{fig:counterExample2}
\end{figure}

\item The lower set~$\linearExtensions(Q,\omega)$ may have more than one maximal element, and~$\omega$ is not necessarily maximal in~$\linearExtensions(Q,\omega)$. See \cref{fig:counterExample1}.

\item Some of the sets~$\linearExtensions(I)$ may not be included in, nor even meet~$[e,\omega]$. See \cref{fig:counterExample1}.
%
%\begin{figure}[h]
%	\includegraphics[width=0.52\textwidth]{interval_not_contained1} \quad
%	\includegraphics[width=0.43\textwidth]{interval_not_contained2}
%	\caption{A facet of a subword complex~$\subwordComplex(Q, \omega)$ whose linear extensions all lie outside the interval~$[e, \omega]$.}
%	\label{fig:outOfInterval}
%\end{figure}
%
\begin{figure}[p]
	\centerline{\includegraphics[scale=.8]{counterExample1}}
	\caption{The sets~$\linearExtensions(I)$ (blue bubbles) are not always subsets of, and may even not meet~$[e,\omega]$ (green bubble).}
	\label{fig:counterExample1}
\end{figure}
\end{enumerate}
Note that \cref{fig:counterExample1,fig:counterExample2} represent type~$A$ subword complexes.
As in~\cite{PilaudPocchiola, PilaudSantos-brickPolytope, PilaudStump-brickPolytope}, we thus use pseudoline arrangements on sorting networks to represent their facets (and we have represented their contact graphs together).
\end{remark}
